Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-03-26 paper/ms.tex
continuing to work on the discussion

{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}. Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, independent of whether or not magnetic inhibition of convection is considered. In the absence of a convective envelope, magnetic inhibition of convection is irrelevant. Therefore, any differences between magnetic and standard stellar model isochrones above this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction). This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone, which occurs near $6\,000$~K in Fig.~\ref{fig:ages}(b). 
It then seems reasonable to posit that the shallow slope of the empirical HR diagram traces the demise of surface convection zones, the weakening of surface magnetic dynamo action, and the growth of radiative cores in young, pre-main-sequence stars.}

>>>>

{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}. Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, independent of whether or not magnetic inhibition of convection is considered. In the absence of a convective envelope, magnetic inhibition of convection is irrelevant. Therefore, any differences between magnetic and standard stellar model isochrones above this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction). This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone near $6\,000$~K in Fig.~\ref{fig:ages}(b). 
It then seems reasonable to posit that the slope of the empirical HR diagram in this temperature domain contains information about the demise of surface convection zones, the growth of radiative cores, and the weakening of surface magnetic dynamo action in young, pre-main-sequence stars.}

{\bf The beginning of the transition between 4\,500 and 5\,000 K corresponds to magnetic models masses of 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$. Magnetic models predict that these stars have radiative core masses between 75\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a). The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} predicts that 1.40 $M_{\odot}$ stars are beginning to enter a brief period of radius inflation that accompanies the ignition of CN-cycle burning \citep{Iben1965}. Photospheric gas pressures rapidly drop during this phase of evolution. A rapid drop in photospheric gas pressure will bring about a rapid drop in surface equipartition magnetic field strengths. As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{fig:equip_values} beginning around 1.40 $M_{\odot}$. Stars above 1.40 $M_{\odot}$ then become less sensitive to magnetic inhibition of convection because the magnetic fields are intrinsically weaker.}

{\bf However, disagreement between model predictions and the properties observed for F-type stars raises concerns that }

{\bf
Figure~\ref{fig:rad_core} compares predictions of radiative core masses as a function of stellar mass and effective temperature from standard models at 5 and 10 Myr (characteristic ages for cool and warm stars) and from magnetic models at 10 Myr. As a function of mass, magnetic models predict stars to have small radiative cores at 10 Myr, a result of delayed contraction. Stars of a given mass take longer to contract down the Hayashi track when magnetic inhibition of convection is included. Core temperatures required to initiate the formation of a radiative core are thus delayed. 
}

{\bf However, when comparing radiative core masses as a function of effective temperature, stars of a given effective temperature have significantly larger radiative core masses when magnetic fields are included.
}
